Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/paper.tex
Manuel's changes
updates paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{xspace}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the Performance and Energy Efficiency of the
  COSMO-ART model system}
%\thanks{}
%\subtitle{}

@@

\begin{abstract}
  In this  paper we investigate  the energy footprint  and performance
  profiling of COSMO-ART  on various HPC platforms.  This  model is an
  extension of  the operational weather  forecast model of  the German
  weather  service   (DWD),  developed  for  the   evaluation  of  the
  interactions of reactive gases  and aerosol particles with the state
  of atmosphere at the  regional scale.  Different measurement devices
  and energy-aware techniques are  described to evaluate both time and
  energy  to  solution  of  the  considered application  and  to  gain
  detailed  insights  into power  and  performance requirements.   Our
  motivation  is to  improve  corresponding code  sections to  sustain
  performance  while minimising energy-to-solution.   This preliminary
  work  sets the  basis for  subsequent studies  to  tackle challenges
  related  to  energy  efficient  high performance  computing  in  the
  framework of the Exa2Green project (\url{http://exa2green.eu/}).

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark    analysis   \and    COSMO-ART    coupled   model    \and
  Time-to-solution \and Energy-to-solution \and Xeon processor}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{Related work \emph{(to be completed)}}
\label{sec:1}
\input{Sec1:Related.tex}

\section{The COSMO-ART model system}
\label{sec:2}
\input{Sec2:COSMO-ART.tex}

\section{Power-performance measurement framework}
\label{sec:3}
\input{Sec3:Measurement-framework.tex}

\section{Evaluation}
\label{sec:4}
\input{Sec4:Evaluation.tex}

\section{Conclusion \emph{(to be completed)}}
\label{concl}
\input{Conclusion.tex}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{colortbl}
\usepackage{xspace}
%
\DeclareRobustCommand\IPCClongname{}
\setcounter{secnumdepth}{5}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the Performance and Energy Efficiency of the
  \textsc{COSMO-ART} model system}
%\thanks{}
%\subtitle{}

@@

\begin{abstract}
  In this  paper we investigate  the energy footprint  and performance
  profiling  of  \textsc{COSMO-ART} on  various  HPC platforms.   This
  model is an  extension of the operational weather  forecast model of
  the German  weather service (DWD),  developed for the  evaluation of
  the interactions  of reactive gases  and aerosol particles  with the
  state of  atmosphere at  the regional scale.   Different measurement
  devices and  energy-aware techniques are described  to evaluate both
  time and  energy to  solution of the  considered application  and to
  gain detailed insights into power and performance requirements.  Our
  motivation  is to  improve  corresponding code  sections to  sustain
  performance  while minimising energy-to-solution.   This preliminary
  work  sets the  basis for  subsequent studies  to  tackle challenges
  related  to  energy  efficient  high performance  computing  in  the
  framework of the Exa2Green project \citep{EXA2GREEN}.

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark  analysis  \and   \textsc{COSMO-ART}  coupled  model  \and
  Time-to-solution \and Energy-to-solution \and Xeon processor}
% \PACS{PACS code1 \and PACS code2 \and more} 
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{Related work}
\label{sec:1}
\input{Sec1:Related.tex}

\section{The \textsc{COSMO-ART} model system}
\label{sec:2}
\input{Sec2:COSMO-ART.tex}

\section{Environment setup}
\label{sec:3}
\input{Sec3:Environment-setup.tex}

\section{Experimental results}
\label{sec:4}
\input{Sec4:Experimental-results.tex}

\section{Conclusion}
\label{concl}
\input{Conclusion.tex}
